Procedural generation of levels fot he angry birds videogame using evolutionary computation\\

### 2019-05-14 article_english.tex
Mini-intro reviewed

\begin{IEEEkeywords}
genetic algorithm, procedural generated content, open-ended evolution,
evolutionary computa
\end{IEEEkeywords}

\section{Introduction}
Procedural content generation is an interesting subject on the entertainment
area, primarily in the video game industry because of the easines and quickness
provided to generate content for diferent video game projects, in this project a
evolutionary computation-based system is proposed to generate complex content
for videogames based on an evolutionary algorithm and open-ended- evolution.

For this project a procedural generation content system is proposed for the game
angly birds, angry birds is a game developed by Rovio Entrtainment in which the
objective is to destroy structures placed on the map as well as eliminating
green pig-like entities in order to obtain the highest score possible, the game
mechanics is to use a slingshot to shoot a certain number of birds with
different abilities to destroy the structures and the objectives.
\cite{RovioEntertainmentCorporation2009}

While it is possible to create a evolutionary agent to play the levels and
obtain the best score the main objective of this project is to generate the
levels can ca be played by the agents or physical players, the levels themselves
need to be complex in the sense that interesting structures can be created but
it has to be possible to complete in some way.

In Section 2, a background of the subjects used on this project will be
presented, this subjects, while not all being used on by different authors on
their works provide a great help on the development of the proposed system,
Section 3, contains a quick overview of some aspects used by different authors
in order to tackle this problem, their design and basic functionality, in
Section 4 the description of the current state of the project is explained, from
the basis of the development to the diferent menthods that have been used to
progress on the different sections of the project, in Section 5 we explain the
future work of the project, where we are in the development phase and how the
future implementations are to further improve the project and finally, in
Section 6 we present our conclusions

>>>>

\begin{IEEEkeywords}
genetic algorithm, procedural generated content, open-ended evolution,
evolutionary computation
\end{IEEEkeywords}

\section{Introduction}
Procedural content generation is an interesting subject on the entertainment
industry, primarily in the video game development because of the easines and
quickness provided to generate content for diferent video game projects [ref] .
In this paper an evolutionary content generation system is proposed to generate
levels for the popular Angry Birds video game
\cite{RovioEntertainmentCorporation2009}, taking inspiration in concepts of
open-ended evolution.

% This paragraph is redundant only uncomment if space is abundant - M

%For this project a procedural generation content system is proposed for the game
%angly birds, angry birds is a game developed by Rovio Entrtainment in which the
%objective is to destroy structures placed on the map as well as eliminating
%green pig-like entities in order to obtain the highest score possible, the game
%mechanics is to use a slingshot to shoot a certain number of birds with
%different abilities to destroy the structures and the objectives.

% I don't think this paragraph adds much
While it is possible to create an evolutionary agent to play the levels and
obtain the best score,  the main objective of this project is to generate the
levels can ca be played by software agents or real players, the levels themselves
need to be complex in the sense that interesting structures can be created but
it has to be possible to complete in some way.

% What is the problem?
% How we solve it? (summary)   
% What is learned?

In Section 2, a background of the subjects used on this project will be
presented, this subjects, while not all being used on by different authors on
their works provide a great help on the development of the proposed system,

% Jaime, remember there is no Background need it in this type of paper 
% Maybe that will be the introduction - M

Section 3, contains a quick overview of some aspects used by different authors
in order to tackle this problem, their design and basic functionality, in
Section 4 the description of the current state of the project is explained, from
the basis of the development to the diferent menthods that have been used to
progress on the different sections of the project, 
% Normaly there is no "Future Work" section is put together with Conclusions - MG
in Section 5 we explain the
future work of the project, where we are in the development phase and how the
future implementations are to further improve the project and finally, in
Section 6 we present our conclusions
